\papertitle

### 2012-10-11 manuscript.tex
Fixed intro type and updated ornithopter platform sections.

% AAMAS 2013 Manuscript
%
% This file should be compiled with "aamas2013.cls" 
% ----------------------------------------------------------------------
% REMEMBER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STYLE NOTES
%
% TENSE AND VOICE: WE WRITE ALL TEXT IN PRESENT TENSE, FIRST PERSON PLURAL ("we")
% CONVENTIONS: flapping-wing, small-scale, lightweight, MAV

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SETUP
\documentclass{aamas2013}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs offer the promise of superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
%TODO(humphrey)
The flying platform used in this experiment is the H$^2$Bird flapping wing 
MAV. Built around the Silverlit I-Bird RC flyer power train and clap-fling 
wings, the H$^2$Bird has a wingspan of [40?] cm and has a flight weight of 
13 grams. A tail propeller and servo-controlled tail elevator provide 
control in the yaw and pitch axes. An on-board electronics package comprises 
a 40 MIPS microprocessor, 6 DOF IMU, IEEE 802.15.4 radio, VGA camera, and motor 
drivers with a 90 mAh lithium polymer battery for autonomous flight. In 
routine flight, the H$^2$Bird averages [insert speed] m/s ground speed and 
can operate for approximately 10 minutes.

@@

Rudimentary attitude control for the H$^2$Bird runs on-board. It estimates 
pose by naively integrating the IMU and depending on PID for control. The 
simplistic nature of our state estimation and control is due to the 
stringent resource constraints applied by the platform.

We use simple controllers to actuate the H$^2$Bird's wing beat frequency, 
tail rotor, and tail elevator, which we designed to actuate thrust, yaw, 
and pitch respectively.

Due to the high pitch angles experienced by the H$^2$Bird, we use a 
quaternion representation of vehicle pose to avoid the numerical 
instabilities of Euler angle representations. This choice of pose 
representation also lends itself well to remote guidance, as relative body 
and world coordinate angular displacements can be represented compactly 
with quaternion multiplication.~\cite{bowman:reasoning}

Given a reference pose $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose. We then 
linearise the error quaternion to produce body axis angular errors as as 
inputs to the attitude controllers.

Three independent proportional-integral-derivative controllers commanding 
the wing thrust, elevator, and tail propeller. We use this independent PID 
controller architecture for simplicity in tuning and implementation, and 
because it demonstrates acceptable performance in the absence of a system 
model.

@@

%% ACM needs 'a single self-contained file'!
%\subsection{References}
%% Generated by bibtex from your ~.bib file.  Run latex,
%% then bibtex, then latex twice (to resolve references)
%% to create the ~.bbl file.  Insert that ~.bbl file into
%% the .tex source file and comment out
%% the command \texttt{{\char'134}thebibliography}.
\end{document}

>>>>

% AAMAS 2013 Manuscript

% This file should be compiled with "aamas2013.cls" 
% ----------------------------------------------------------------------
% REMEMBER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
% ----------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STYLE NOTES
%
% TENSE AND VOICE
% * Actual experimental events
% 	We wrote descriptions of actual experimental events using past tense, in 
%	active voice, as the first person plural.
%
% * All other contexts
%	We write all other text using present tense, in active voices, as the
%	the first person plural.  
%
% CONVENTIONS
% flapping-wing, small-scale, lightweight, MAV
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SETUP
\documentclass{aamas2013}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
%TODO(humphrey)
The flying platform used in this experiment is the H$^2$Bird flapping wing 
MAV. Built around the Silverlit I-Bird RC flyer power train and clap-fling 
wings, the H$^2$Bird has a wingspan of [40?] cm and has a flight weight of 
13 grams. A tail propeller and servo-controlled tail elevator provide 
control in the yaw and pitch axes. The on-board electronics package consists of 
a 40 MIPS microprocessor, 6 DOF IMU, IEEE 802.15.4 radio, VGA camera, and motor 
drivers with a 90 mAh lithium polymer battery. In routine flight, the H$^2$Bird 
averages [1.2 m/s] and can operate for approximately 10 minutes.

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
acceptable tracking performance. We estimate the vehicle pose by naively
integrating the IMU, and use PID for controlling the vehicle. The simplistic 
nature of our approach arises from the stringent resource constraints 
of our platform, but nonetheless is not a completely trivial implementation.

One characteristic of the H$^2$Bird that separates it from other MAVs is the
high pitch angles experienced in routine flight. An Euler angle 
parameterization of the vehicle orientation would suffer from singularities
around these high pitch angles, so we instead represent the vehicle orientation
with quaternions. An additional benefit of the quaternion representation is 
the ability to represent relative body and world coordinate angular displacements 
compactly with quaternion multiplication.~\cite{bowman:reasoning}

Given a reference quaternion $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose. We then 
convert this error quaternion to an angle axis representation which is given
as an input to the PID controller.

@@

% ACM needs 'a single self-contained file'!
%\subsection{References}
% Generated by bibtex from your ~.bib file.  Run latex,
% then bibtex, then latex twice (to resolve references)
% to create the ~.bbl file.  Insert that ~.bbl file into
% the .tex source file and comment out
% the command \texttt{{\char'134}thebibliography}.
\end{document}
